High-Throughput Phenotyping using Computer Vision and Machine Learning \\ \large SMC Data Challenge \#1

### 2023-10-04 paper/main.tex
better display?
built new verison of paper

Traditionally, plant morphologies would be analyzed manually, wasting time and potentially damaging the environment. However, current breakthroughs in high-throughput phenotyping led by machine learning techniques\citep{koh2021automated, pound2017deep} and computer vision with deep learning \citep{mochida2019computer} have allowed for efficient and timely analyses of plant phenotypes. With these methods, researchers can extract features from plants and classify their morphologies effectively while having little effect on the plant itself.

@@

Advancements in the field of plant phenotyping have been pioneered by technology. From using hardware, such as Raspberry Pi imaging systems \citep{tausen2020greenotyper} to thermographic sensing techniques \citep{walter2015plant}, research in the field of high-throughput phenotyping has led to an acceleration in working efficiency. Plants are now able to be analyzed in fast, effective, and accurate methods allowing for them to be used in scientific discoveries. In our study, we rely on machine learning techniques to classify morphologies based on a phone image dataset provided.

@@

\begin{center}
	\centering
	\includegraphics[width=0.23\textwidth]{images/seg_pipeline/6.png}	
        \includegraphics[width=0.23\textwidth]{images/seg_filter/2.png}	
	\captionof{figure}{From leaf approximations with image processing to filtered leaf segmentations, from the SAM/ONNX Runtime (green leaves fit for classification)}
	% \label{fig_mom0}%
\end{center}

@@

In the second part of challenge 4, we aimed to find a correlation between phenotypes and environmental features, such as soil type and weather conditions. Using the EXIF tags, we were able to retrieve the coordinates where the image was taken. We noticed all of the images contained were taken in approximately the same location, so any weather or soil API would be unable to provide specific conditions. If we were given this information as part of the dataset, we would have been better able to find correlations. Regardless, a study on how the temperature affects the phenotype and development plasticity in Arabidopsis Thaliana \citep{ibanez2017ambient} placed the plants in different temperature environments in order to measure their differences. If we had more information regarding the conditions in which the plants were raised, we would be better able to determine if there was a correlation between phenotypes and environment.

@@

Future research could be done in expanding the species analyzed for morphology classifications. In this study, only Populus Trichocarpae were used, so the models used may only be effective on this species.

Since a pretrained segmentation model (the SAM) was used in this study, researchers could attempt to build segmentation models fine-tuned to only recognize leaves, which could increase model efficiency and provide more consistent results.

@@

\newpage
\appendix

>>>>

Traditionally, plant morphologies would be analyzed manually, wasting time and potentially damaging the environment. However, current breakthroughs in high-throughput phenotyping led by machine learning techniques \citep{koh2021automated, pound2017deep} and computer vision with deep learning \citep{mochida2019computer} have allowed for efficient and timely analyses of plant phenotypes. With these methods, researchers can extract features from plants and classify their morphologies effectively while having little effect on the plant itself.

@@

Advancements in the field of plant phenotyping have been pioneered by technology. From using hardware, such as Raspberry Pi imaging systems \citep{tausen2020greenotyper} to thermographic sensing techniques \citep{walter2015plant}, research in the field of high-throughput phenotyping has led to an acceleration in working efficiency. Plants are now able to be analyzed in fast, effective, and accurate methods allowing for them to be used in scientific discoveries. In our study, we rely on machine learning techniques to classify morphologies based on a plant image dataset provided.

@@

\begin{center}
	\centering
	\includegraphics[width=0.23\textwidth]{images/seg_pipeline/6.png}	
        \includegraphics[width=0.23\textwidth]{images/seg_filter/2_better.png}	
	\captionof{figure}{From leaf approximations with image processing to filtered leaf segmentations, from the SAM/ONNX Runtime (green leaves fit for classification)}
	% \label{fig_mom0}%
\end{center}

@@

In the second part of challenge 4, we aimed to find a correlation between phenotypes and environmental features, such as soil type and weather conditions. Using the EXIF tags, we were able to retrieve the coordinates where the image was taken. However, we noticed all of the images contained were taken in approximately the same location.

\begin{center}
    \includegraphics[width=0.45\textwidth]{images/plant_locs.png}
    \captionof{figure}{Geographical plot of all plants using encoded EXIF GPS data.}
\end{center}

Therefore, any weather or soil API would be unable to provide specific conditions. If we were given this information as part of the dataset, we would have been better able to find correlations. Regardless, a study on how the temperature affects the phenotype and development plasticity in Arabidopsis Thaliana \citep{ibanez2017ambient} placed the plants in different temperature environments in order to measure their differences. If we had more information regarding the conditions in which the plants were raised, we would be better able to determine if there was a correlation between phenotypes and environment.

@@

Future research could be done to expand the species analyzed for morphology classifications. In this study, only Populus Trichocarpae were used, so the models used may only be effective on this species.

Since a pre-trained segmentation model (the SAM) was used in this study, researchers could attempt to build segmentation models fine-tuned to only recognize leaves, which could increase model efficiency and provide more consistent results.

@@

\clearpage
\appendix
